Postural changes mediate children's visual access to faces and hands

### 2018-01-11 writeup-cogsci/cogsci2018.tex

\title{Developmental and postural changes in children's visual access to faces}

@@

\begin{figure*}
\includegraphics[width=6in]{images/framesample.pdf}
\caption{\label{fig:frames} Sample frames from the headcam videos for a child from each age group, selected because they featured successful face detections (green squares).}
\end{figure*}

All headcam videos were cropped to exclude the period of entry to the
playroom and were automatically synchronized with the tripod-mounted
videos using FinalCut Pro Software. These sessions yielded a substantial
amount of video: a total of 516 minutes (almost a milion frames), with
an average video length of 8.6 minutes (min = 4.53, max = 19.35).

@@

We report results from three different sets of analyses. First, we
explore developmental changes in posture and orientation in our dataset.
Next, we explore how these changes affect access to faces and to hands,
as measured using computater vision algorithms. Finally, we explore how
these changes impact the accessibility of faces and hands during
labeling events.

\subsection{Changes in Posture and
Orientation}\label{changes-in-posture-and-orientation}

\subsection{Changes in Access to
Faces}\label{changes-in-access-to-faces}

\subsection{Changes in Access to
Hands}\label{changes-in-access-to-hands}

>>>>

\title{Postural changes mediate children's visual access to faces and hands}

@@

\begin{figure*}
\includegraphics[width=6in]{images/framesample.pdf}
\caption{\label{fig:frames} Example face detections made by MTCNN for the headcam videos from a child in each group  (green squares).}
\end{figure*}

Headcam videos were trimmed such that they excluded the instruction
phase when the experimenter was in the room and were automatically
synchronized with the tripod-mounted videos using FinalCut Pro Software.
These sessions yielded videos of 516 minutes (almost a milion frames),
with an average video length of 8.6 minutes (min = 4.53, max = 19.35).

@@

We report results from three different sets of analyses. First, we
explore how these changes affect access to faces and to hands, as
measured using computater vision algorithms. Second, we explore how
these changes impact the accessibility of faces and hands during
labeling events.

\section{Changes in Access to Faces}\label{changes-in-access-to-faces}

{\centering \includegraphics{figs/unnamed-chunk-3-1}

\caption[R plot]{R plot}\label{fig:unnamed-chunk-3}
\end{figure}
\end{CodeChunk}

{\centering \includegraphics{figs/unnamed-chunk-4-1}

\caption[R plot]{R plot}\label{fig:unnamed-chunk-4}
\end{figure}
\end{CodeChunk}

{\centering \includegraphics{figs/unnamed-chunk-5-1}

\caption[R plot]{R plot}\label{fig:unnamed-chunk-5}
\end{figure}
\end{CodeChunk}

\section{Changes in Access to Hands}\label{changes-in-access-to-hands}
